### 2025-07-19 evaluating-prediction-accuracy.qmd
20250719 - descriptive text

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points,
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points,
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Here are the seasonal accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., the players that are most important to differentiate between):
```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

Here are the seasonal accuracy indexes for all Quarterbacks:
```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points,
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

A calibration plot of the seasonal projections for Quarterbacks is in @fig-calibrationPlotSeasonalQBs.
```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

Here are the seasonal accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., the players that are most important to differentiate between):
```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

Here are the seasonal accuracy indexes for all Running Backs:
```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points,
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

A calibration plot of the seasonal projections for Running Backs is in @fig-calibrationPlotSeasonalRBs.
```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a locally estimated scatterplot smoothing (LOESS) model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

Here are the seasonal accuracy indexes for only those Running Backs who had high projected or actual points (i.e., the players that are most important to differentiate between):
```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

@@

Here are the seasonal accuracy indexes for all Wide Receivers:

@@

A calibration plot of the seasonal projections for Wide Receivers is in @fig-calibrationPlotSeasonalWRs.

@@

Here are the seasonal accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the seasonal accuracy indexes for all Tight Ends:

@@

A calibration plot of the seasonal projections for Tight Ends is in @fig-calibrationPlotSeasonalTEs.

@@

Here are the seasonal accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the seasonal accuracy indexes for all Kickers:

@@

A calibration plot of the seasonal projections for Kickers is in @fig-calibrationPlotSeasonalKs.

@@

Here are the seasonal accuracy indexes for only those Kickers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the seasonal accuracy indexes for all Defensive Linemen:

@@

A calibration plot of the seasonal projections for Defensive Linemen is in @fig-calibrationPlotSeasonalDLs.

@@

Here are the seasonal accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the seasonal accuracy indexes for all Linebackers:

@@

A calibration plot of the seasonal projections for Linebackers is in @fig-calibrationPlotSeasonalLBs.

@@

Here are the seasonal accuracy indexes for only those Linebackers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the seasonal accuracy indexes for all Defensive Backs:

@@

A calibration plot of the seasonal projections for Defensive backs is in @fig-calibrationPlotSeasonalDBs.

@@

Here are the seasonal accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all players (across all positions):

@@

A calibration plot of the weekly projections for all players (across all positions) is in @fig-calibrationPlotWeeklyOverall.

@@

Here are the weekly accuracy indexes for players across all positions, but only among those who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Quarterbacks:

@@

A calibration plot of the weekly projections for Quarterbacks is in @fig-calibrationPlotWeeklyQBs.

@@

Here are the weekly accuracy indexes for only those Quarterbacks who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Running Backs:

@@

A calibration plot of the weekly projections for Running Backs is in @fig-calibrationPlotWeeklyRBs.

@@

Here are the weekly accuracy indexes for only those Running Backs who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Wide Receivers:

@@

A calibration plot of the weekly projections for Wide Receivers is in @fig-calibrationPlotWeeklyWRs.

@@

Here are the weekly accuracy indexes for only those Wide Receivers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Tight Ends:

@@

A calibration plot of the weekly projections for Tight Ends is in @fig-calibrationPlotWeeklyTEs.

@@

Here are the weekly accuracy indexes for only those Tight Ends who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Kickers:

@@

A calibration plot of the weekly projections for Kickers is in @fig-calibrationPlotWeeklyKs.

@@

Here are the weekly accuracy indexes for only those Kickers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Defensive Linemen:

@@

A calibration plot of the weekly projections for Defensive Linemen is in @fig-calibrationPlotWeeklyDLs.

@@

Here are the weekly accuracy indexes for only those Defensive Linemen who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Linebackers:

@@

A calibration plot of the weekly projections for Linebackers is in @fig-calibrationPlotWeeklyLBs.

@@

Here are the weekly accuracy indexes for only those Linebackers who had high projected or actual points (i.e., the players that are most important to differentiate between):

@@

Here are the weekly accuracy indexes for all Defensive Backs:

@@

A calibration plot of the weekly projections for Linebackers is in @fig-calibrationPlotWeeklyDBs.

@@

Here are the weekly accuracy indexes for only those Defensive Backs who had high projected or actual points (i.e., the players that are most important to differentiate between):
